---
title: "Interactive Maps"
author: "RP"
date: "May 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## <span style="color:dark grey"> Introduction </span>

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. 

```{r echo=TRUE}
library(leaflet)

lat <- c(28.444957, 27.024967, 28.054947, 28.474977, 28.094937)
lng <- c(77.321260, 77.321350, 76.323240, 76.325270, 77.327280)
pop <- c(1289,490, 700, 230, 650)
area <- c('Sector 30', 'Sector 29', 'Sector 19', 'Sector 28', 'Sector 88')

my_df <- data.frame(lat, lng, pop, area)
```

- Create a dataframe `my_df` to have latitude, longitude, Population and area name.

**Next we will show the area wise population in Millions**

## <span style="color:dark grey"> Interactive Plot showing the Areawise Population </span>


###`r format(Sys.Date(),'%B %d, %Y')` 

```{r pressure, echo=TRUE}
my_map <- leaflet(my_df) %>% 
  addTiles() %>% 
  addMarkers(lng=my_df$lng, 
           lat=my_df$lat, 
           popup=paste(my_df$area, "<br> Population in Millions: ",
                       formatC(my_df$pop, format = "d")))  %>%
  addCircles(lng    = my_df$lng, 
             lat    = my_df$lat, 
             weight = 1, 
             radius = (my_df$pop * 20), 
             popup  = paste("Area Name is:",strwrap(my_df$area))) 
my_map
```

