---
title: "Motor Trends from MTCARS Dataset"
author: "RP"
date: "May 29, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Motor Trends from MTCARS Dataset

1. We will check MPG on Manual V/S Automatic transmission.
2. We will check MPG on Cylinder with number of gears.

Below are the elements in **mtcars** dataset.

   - mpg	  :  Miles/(US) gallon
   - cyl	  :  Number of cylinders
   - disp   :  Displacement (cu.in.)
   - hp	    :  Gross horsepower
   - drat   :  Rear axle ratio
   - wt	    :  Weight (1000 lbs)
   - qsec   :  1/4 mile time
   - vs	    :  Engine (0 = V-shaped, 1 = straight)
   - am	    :  Transmission (0 = automatic, 1 = manual)
   - gear   :  Number of forward gears
   - carb   :  Number of carburetors

## <span style="color:grey"> Cars Mileage highlighting Automatic and Manual Transmission </span>
###`r format(Sys.Date(),'%B %d, %Y')` 
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)
data("mtcars")

mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$gear <- as.factor(mtcars$gear)
mtcars$carb <- as.factor(mtcars$carb)
mtcars$am <- as.factor(mtcars$am)
mtcars$am <- ifelse(mtcars$am == 0,"Automatic", "Manual")
mtcars$car <- rownames(mtcars)

plot_ly(mtcars, x=mtcars$car, y=mtcars$mpg, mode="markers", color = mtcars$am) 
```


## <span style="color:grey"> Mileage based on the weight of Car and horse power  </span>
###`r format(Sys.Date(),'%B %d, %Y')` 
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)

plot_ly(mtcars , x=mtcars$wt, y=mtcars$mpg, mode="markers", color = as.factor(mtcars$cyl), 
        size = (mtcars$hp))
 
```

## <span style="color:grey"> Thankyou  </span>


